---
title: "A3: SPL Library Checkouts"
output: html_document
---

```{r setup, include=FALSE}
library("knitr")
source("summary.R")
```

### Introduction

This data described the number of checkout materials both in digital and 
physical forms that has been checked out by individuals from 2017 to 2023 with
items checked out at least 10 times a month.
I especially liked the book The Hobbit, because not only did I read the book
thoroughly, but also watched the movie a few times. The plots and settings of 
the data are innovative and just feels different to other movies or novels. So 
I did some investigations to analyze the trends and some interesting information
of the book.  

### Summary Information

The development of technology with recent COVID cases drastically impacted 
society, pushed public interest from physical hard copies to digital electronic 
copies of files. From a data published by the Seattle government, I found that 
digital copies in 2017 is `r digital_ratio_2017` percent of total checkouts. 
Going into 2022, the digital copies increased to `r digital_ratio_2022` percent 
of total checkouts. Being extremely interested in the book The hobbit, I found 
that the year with the most checkouts for The hobbit is 
`r most_checkout_year_hobbit`, and the least being 
`r least_checkout_year_hobbit`. The year with the most checkout for ebooks is `r most_checkout_year_ebook`.

### The Dataset

This data is collected and published by the Seattle Public Library, 
for public information. The parameters of the data are pretty wide, including 
12 columns in total, each representing usage class, denotes if item is physical 
or digital, checkout type, denotes the vendor tool used to checkout the item, 
material type, describes the type of item checked out, checkout year, checkout 
month, checkouts, title, ISBN, creator, subjects, publisher and publication 
year. The data was generated by the Seattle Public Library system, so that 
each checkout by individual would leave a mark in the system to be calculated 
in the data. The inspiration for this data includes better logistics modeling, 
and predicting books that would be checked out in the coming month. One 
possible ethical question that might come up while working with this data 
would be invasion on privacy. Many individuals might not want this information 
to be disclosed to the public, even if its anonymous. Possible problems could 
include the size of the data, being too big for many PC's to operate normally, 
and might encourage individuals to borrow checkout materials from a certain 
source because of its popularity. In addition, some of the borrowed books that 
have not been returned have not been calculated into this data set, which might 
pose some deviations if those books were returned and checked out by other 
individuals. 

### First Trends Over Time Chart

The first chart was included because I was wondering how COVID and development 
of technology affected people's style in checkouts. The plot described the 
trend over time in total checkout for different usage class, and showed that 
as physical checkouts decreased overtime, digital checkouts rose heavily from 
January 2017, taking 64.19 percent of total checkouts.

``````{r, echo = FALSE, warning = FALSE, code = readLines("chart1.R")}
```

### Second Trends Over Time Chart

The second chart shows interesting trends on total checkouts by different 
material types. This was included because I wanted to discover how people change 
their checkout habits in response to advancements in technology and COVID. The 
plot shows that magazines and movies are pretty much eliminated after January 
2019, while Ebooks shows a consistent rise in interest as time progresses. 
In addition, physical copies of books have fallen dramatically during mid 2020s,
but slowly risen back up as COVID ends.

``````{r, echo = FALSE, warning = FALSE, code = readLines("chart2.R")}
```

### Your Choice

The last chart is up to you. It could be a line plot, scatter plot, histogram, bar plot, stacked bar plot, and more. Here are some requirements to help guide your design:

- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear legend title

Here's an example of how to run an R script inside an RMarkdown file:

``````{r, echo = FALSE, warning = FALSE, code = readLines("chart3.R")}
```


