---
title: "A3: SPL Library Checkouts"
output: html_document
---

```{r setup, include=FALSE}
library("knitr")
source("summary.R")
```

### Introduction

This data described the number of checkout materials both in digital and 
physical forms that has been checked out by individuals from 2017 to 2023 with
items checked out at least 10 times a month.
I especially liked the book The Hobbit, because not only did I read the book
thoroughly, but also watched the movie a few times. The plots and settings of 
the data are innovative and just feels different to other movies or novels. So 
I did some investigations to analyze the trends and some interesting information
of the book.  

### Summary Information

Write a summary paragraph of findings that includes the 5 values calculated from your summary information R script

These will likely be calculated using your DPLYR skills, answering questions such as:

- What is the average number of checkouts for each item?
- What is the month or year with the most/least checkouts for a book that you're interested in?
- What is the month or year with the most/least checkouts for ebooks?
- How has the number of print book checkouts changed over time?

Feel free to calculate and report values that you find relevant.

### The Dataset

This data is collected and published by the Seattle Public Library, 
for public information. The parameters of the data are pretty wide, including 
12 columns in total, each representing usage class, denotes if item is physical 
or digital, checkout type, denotes the vendor tool used to checkout the item, 
material type, describes the type of item checked out, checkout year, checkout 
month, checkouts, title, ISBN, creator, subjects, publisher and publication 
year. The data was generated by the Seattle Public Library system, so that 
each checkout by individual would leave a mark in the system to be calculated 
in the data. The inspiration for this data includes better logistics modeling, 
and predicting books that would be checked out in the coming month. One 
possible ethical question that might come up while working with this data 
would be invasion on privacy. Many individuals might not want this information 
to be disclosed to the public, even if its anonymous. Possible problems could 
include the size of the data, being too big for many PC's to operate normally, 
and might encourage individuals to borrow checkout materials from a certain 
source because of its popularity. In addition, some of the borrowed books that 
have not been returned have not been calculated into this data set, which might 
pose some deviations if those books were returned and checked out by other 
individuals. 

### First Trends Over Time Chart

The first chart was included because I was wondering how COVID and development 
of technology affected people's style in checkouts. The plot described the 
trend over time in total checkout for different usage class, and showed that 
as physical checkouts decreased overtime, digital checkouts rose heavily from 
January 2017, taking 64.19 percent of total checkouts.

``````{r, echo = FALSE, warning = FALSE, code = readLines("chart1.R")}
```

### Second Trends Over Time Chart

Include a chart. Make sure to describe why you included the chart, and what patterns emerged

The second chart that you will create and include will show another trend over time of your variable/topic/interest. Think carefully about what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Show more than one, but fewer than ~10 trends
  - For example, two books, or 5 different mediums
- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear - legend title
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

When we say "clear" or "human readable" titles and labels, that means that you should not just display the variable name.

Here's an example of how to run an R script inside an RMarkdown file:

``````{r, echo = FALSE, warning = FALSE, code = readLines("chart2.R")}
```

### Your Choice

The last chart is up to you. It could be a line plot, scatter plot, histogram, bar plot, stacked bar plot, and more. Here are some requirements to help guide your design:

- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear legend title

Here's an example of how to run an R script inside an RMarkdown file:

``````{r, echo = FALSE, warning = FALSE, code = readLines("chart3.R")}
```


